Dominance Regions for Rank Two Cluster Algebras

### 2022-03-28 dominance_regions.tex
Finished typing Theorem 1.4, other random edits.

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}

@@

  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
  We will therefore assume that $bc\ge4$.
  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\lambda+(b\ZZ\oplus c\ZZ)$-lattice points in its \emph{dominance polygon}.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$ inside its \emph{dominance polygon} for integers $a_1,a_2$.
  %In this case, we compute the possible transitions between any two pointed bases.
  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
  \begin{theorem}
    The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
    {
      \everymath={\displaystyle}
      \def\arraystretch{2.8}
      \[
        \begin{array}{rcccl}
          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
          \\
          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
          \\
          0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
          \\
          \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
        \end{array}
      \]
    }
  \end{theorem}

@@

  \begin{theorem}
    There are six classes of dominance polytopes.
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cC(\lambda)$ is the point $\lambda$. 
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}((2-bc)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2)$.
      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cC(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cC(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cC(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,-c\lambda_1+(2-bc)\lambda_2)$.
    \end{enumerate}
  \end{theorem}
  \begin{proof}
    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
    or 
    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
  \end{proof}

@@

@@

  \begin{lemma}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    It is enough to consider $\phi_{t_{-2}}^{-1}\cC(\phi_{t_{-2}}\lambda) \cap \cC(\lambda) \cap \phi_{t_2}^{-1}\cC(\phi_{t_2}\lambda)$, we leave the details to the reader.
  \end{proof}

  \begin{lemma}
    \label{le:one direction}
    For $\lambda\in\cI\cap\ZZ^2$, 
    \begin{enumerate}
      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
    \end{enumerate}
  \end{lemma}
  \begin{proof}
    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
    We first show that $\cC(\lambda) \cap \phi_{t_i}^{-1}\cC(\phi_{t_i}\lambda)\supsetneq \cC(\lambda) \cap \phi_{t_j}^{-1}\cC(\phi_{t_j}\lambda)$ for $0\le i<j$.
  \end{proof}

>>>>

\newcommand{\cA}{\mathcal{A}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cD}{\mathcal{D}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\cQ}{\mathcal{Q}}
\newcommand{\cS}{\mathcal{S}}

@@

  When $bc\le3$, the cluster algebra $\cA(b,c)$ will be of finite-type and cluster monomials form its only pointed basis.
  We will therefore assume that $bc\ge4$.
  In this case we give an explicit description of the dominance relation among $\bfg$-vectors.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\lambda+(b\ZZ\oplus c\ZZ)$-lattice points in its \emph{dominance polygon} $\cP(\lambda)$.
  Specifically, we show that the $\bfg$-vector $\lambda$ dominates precisely the collection of $\bfg$-vectors of the form $\lambda+(b a_1 ,c a_2)$ inside its \emph{dominance polygon} for integers $a_1,a_2$.
  %In this case, we compute the possible transitions between any two pointed bases.
  %The collection of $\bfg$-vectors which can appear in the deformation of a pointed basis is the \emph{dominance region}.
  \begin{theorem}
    The dominance polygon pointed at $\lambda=(\lambda_1,\lambda_2)$ is the region defined by $x\leq \lambda_1, y\geq\lambda_2$, and the following inequalities:
    {
      \everymath={\displaystyle}
      \def\arraystretch{2.8}
      \[
        \begin{array}{rcccl}
          0 & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)+(y-\lambda_2) & \leq & \max\left(-c\lambda_1-\frac{b c+\sqrt{b c (b c-4)}}{2b}b\lambda_2,0\right)
          \\
          \min\left(-c\lambda_1,0\right) & \leq & \frac{b c-\sqrt{b c (b c-4)}}{2 b}(x-\lambda_1)-(y-\lambda_2) & \leq & 0
          \\
          0 & \leq &  -(x-\lambda_1)-\frac{b c-\sqrt{b c (b c-4)}}{2 c}(y-\lambda_2) & \leq & \max\left(\frac{b c+\sqrt{b c (b c-4)}}{2c}c\lambda_1+b\lambda_2,0\right)
          \\
          \min\left(b \lambda_2,0\right) & \leq & (x-\lambda_1) - \frac{b c-\sqrt{b c (b c-4)}}{2 c} (y-\lambda_2) & \leq & 0
        \end{array}
      \]
    }
  \end{theorem}

@@

  \begin{theorem}
    There are six classes of dominance polytopes.
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, i.e. if it is the $\bfg$-vector of a cluster monomial, then $\cP(\lambda)$ is the point $\lambda$. 
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $-\frac{bc+\sqrt{bc(bc-4)}}{2c}\big(\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2,0\big)$, $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(-(bc-2)\lambda_1-b\lambda_2,c\lambda_1+2\lambda_2\big)$.
      \item If $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0\big)$, and $\big(0,\frac{\sqrt{bc(bc-4)}}{b}\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2\big)$.
      \item If $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $\big(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0\big)$, and $\big(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell\big)$.
      \item If $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $\big(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0\big)$, $-\frac{bc+\sqrt{bc(bc-4)}}{2b}\big(0,\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
    \end{enumerate}
  \end{theorem}

@@

  Given a Laurent polynomial in $\ZZ[x_1^{\pm1},x_2^{\pm1}]$, its \emph{support} is the set of its exponent vectors inside $\ZZ^2$.
  \begin{theorem}
    For a $\bfg$-vector $\lambda=(\lambda_1,\lambda_2)\in\ZZ^2$ the support for a pointed basis vector $x_\lambda$ is contained in the (possibly degenerate) lattice quadrilateral $\cS_\lambda$ given as follows:
    \begin{enumerate}
      \item If $\lambda$ lies outside of $\cI$, there are the following possibilities:
        \begin{enumerate}
          \item If $0\le\lambda_1,\lambda_2$, then $\cS_\lambda$ is just the point $\lambda$.
          \item If $\lambda_1 < 0$ and $0\le\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1,-c\lambda_1+\lambda_2)$.
          \item If $\lambda_2 < 0$ and $0\le\lambda_1+b\lambda_2$, then $\cS_\lambda$ is the segment joining $\lambda$ and $(\lambda_1+b\lambda_2,\lambda_2)$.
          \item If $\lambda_1,\lambda_2 < 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(\lambda_1,-c\lambda_1+\lambda_2)$.
          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $-c\lambda_1-(bc-1)\lambda_2\le 0$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\big((bc-1)\lambda_1+(b^2c-2b)\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$.
          \item If $\lambda_1 > 0$, $\lambda_1+b\lambda_2 < 0$, and $0 < -c\lambda_1-(bc-1)\lambda_2$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $(0,0)$.
        \end{enumerate}
      \item If $\lambda$ lies inside of $\cI$, then $\cS_\lambda$ has corner vertices $\lambda$, $(\lambda_1+b\lambda_2,\lambda_2)$, $\big(\lambda_1+b\lambda_2,-c\lambda_1-(bc-1)\lambda_2\big)$, and $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}\big(2\lambda_1+b\lambda_2,-c\lambda_1-(bc-2)\lambda_2\big)$.
    \end{enumerate}
  \begin{theorem}\label{th:Newton polygons}\cite[Proposition~4.1]{LLZ}, \cite[Corollary~3.5]{LLZ2}
  For $(a_1,a_2)\in\ZZ^2$, the smallest (possibly degenerate) lattice quadrilateral $R_{a_1,a_2}$ containing the support of $x[a_1,a_2]$ is determined as follows.
  \begin{enumerate}
    \item If $a_1 \leq 0$ and $a_2 \leq 0$, then $R_{a_1,a_2} = \{(-a_1,-a_2)\}$.
    \item If $a_1 \leq 0 < a_2$, then $R_{a_1,a_2} = \{(p_1,-a_2): -a_1\leq p_1\leq -a_1+ba_2\}$.
    \item If $a_2 \leq 0 < a_1$, then $R_{a_1,a_2} = \{(-a_1,p_2): -a_2 \leq p_2 \leq -a_2+ca_1\}$.
    \item If $0<ba_2\leq a_1$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1+ba_2,\; -a_2\le p_2\le -a_2-cp_1\right\}$.
    \item If $0<ca_1\leq a_2$, then $R_{a_1,a_2}=\left\{(p_1,p_2): -a_1\le p_1\le -a_1-bp_2,\; -a_2\le p_2\le -a_2+ca_1\right\}$.
    \item If $0 < a_1 < ba_2$ and $0 < a_2 < ca_1$, then
    $$\aligned
    R_{a_1,a_2}=&\bigg\{(p_1,p_2)\bigg|\; -a_1\le p_1<0,\; -a_2\le p_2<\Big(\frac{a_2}{a_1}-c\Big)p_1\bigg\}\\
    &\bigcup\bigg\{(p_1,p_2): -a_1\le p_1<\Big(\frac{a_1}{a_2}-b\Big)p_2,\; -a_2\le p_2<0\bigg\}\\
    &\hspace{1.35em}\bigcup\Big\{(-a_1+ba_2,-a_2),(-a_1,-a_2+ca_1)\Big\}.
    \endaligned
    $$
  \end{enumerate}
  Moreover, if $z\in\cA(b,c)$ is pointed at $(a_1,a_2)$ with support contained in $R_{a_1,a_2}$, then $z=x[a_1,a_2]$. 
\begin{figure}[h!]
  \centering
  \begin{tikzpicture}[scale=.7]
    %(1)
    \begin{scope}[shift={(-2.75, 5.5)}]
      \usetikzlibrary{patterns}
      \draw[-] (-0.5,0.25) -- (3,0.25);
      \draw[-] (0,-0.25) -- (0,3);
      \fill[white] (0,0.25) circle (2pt);
      \draw (0,0.25) circle (2pt);
      \draw (0,0.25) node[anchor=south west] {\tiny $O$};
      \fill (1.5,1.75) circle (2pt);
      \draw (1.5,1.75) node[anchor=east] {\tiny $B$};
      \draw (1.07,-.6) node[anchor=north] {\footnotesize (1) $a_1,a_2\le0$};
    \end{scope}
    %(2)
    \begin{scope}[shift={(2.75, 5.5)}]
      \usetikzlibrary{patterns}
      \draw[-] (-0.5,1.5) -- (3,1.5);
      \draw[-] (0,-0.25) -- (0,3);
      \fill[white] (0,1.5) circle (2pt);
      \draw (0,1.5) circle (2pt);
      \draw (0,1.5) node[anchor=south west] {\tiny $O$};
      \fill (2.25,0.5) circle (2pt);
      \draw (2.25,0.5) node[anchor=west] {\tiny$A$};
      \fill (0.75,0.5) circle (2pt);
      \draw (0.75,0.5) node[anchor=east] {\tiny$B$};
      \draw [thick] (0.75,0.5) -- (2.25,0.5);
      \draw (1.27,-.6) node[anchor=north] {\footnotesize (2) $a_1\le 0<a_2$};
    \end{scope}
    %(3)
    \begin{scope}[shift={(8.25,5.5)}]
      \usetikzlibrary{patterns}
      \draw [thick] (0.25,1) -- (0.25,2.5);
      \draw[-] (-0.5,0.25) -- (3,0.25);
      \draw[-] (1,-0.25) -- (1,3);
      \fill[white] (1,0.25) circle (2pt);
      \draw (1,0.25) circle (2pt);
      \draw (1,0.25) node[anchor=south west] {\tiny $O$};
      \fill (0.25,1) circle (2pt);
      \draw (0.25,1) node[anchor=east] {\tiny$B$};
      \fill (0.25,2.5) circle (2pt);
      \draw (0.25,2.5) node[anchor=east] {\tiny$C$};
      \draw (1.27,-.6) node[anchor=north] {\footnotesize (3) $a_2\le0<a_1$};
    \end{scope}
    %(4)
    \begin{scope}[shift={(0,0)}]
      \usetikzlibrary{patterns}
      \fill[black!10] (0,3)--(1.5,1.5)--(1.5,0)--(0,0)--(0,3);
      \draw[thick] (0,3)--(1.5,1.5)--(1.5,0)--(0,0)--(0,3);
      \draw[dashed,thick](0,3)--(2.15,1.25) (2.15,1.15)--(1.5,0);
      \draw[-] (-0.5,1.2) -- (3.5,1.2);
      \draw[-] (2.2,-0.25) -- (2.2,3.5);
      \fill[white] (2.2,1.2) circle (2pt);
      \draw (2.2,1.2) circle (2pt);
      \draw (2.2,1.2) node[anchor=north west] {\tiny$O$};
      \fill (1.5,0) circle (2pt);
      \draw (1.5,0) node[anchor=west] {\tiny$A$};
      \fill (0,0) circle (2pt);
      \draw (0,0) node[anchor=east] {\tiny$B$};
      \fill (0,3) circle (2pt);
      \draw (0,3) node[anchor=east] {\tiny$C$};
      \fill (1.5,1.5) circle (2pt);
      \draw (1.5,1.5) node[anchor=east] {\tiny$D_1$};
      \draw (1.37,-0.5) node[anchor=north] {\footnotesize (4) $0<ba_2\leq a_1$};
    \end{scope}
    %(5)
    \begin{scope}[shift={(5.5,0)}]
      \usetikzlibrary{patterns}
      \fill[black!10] (3,0)--(1.3,1)--(0,1)--(0,0)--(3,0);
      \draw[thick] (3,0)--(1.3,1)--(0,1)--(0,0)--(3,0);
      \draw[dashed,thick](3,0)--(0.75,1.75)--(0,1);
      \draw[-] (-0.5,1.75) -- (3.5,1.75);
      \draw[-] (0.75,-0.25) -- (0.75,3.5);
      \fill[white] (0.75,1.75) circle (2pt);
      \draw (0.75,1.75) circle (2pt);
      \draw (0.75,1.75) node[anchor=south west] {\tiny$O$};
      \fill (3,0) circle (2pt);
      \draw (3,0) node[anchor=west] {\tiny$A$};
      \fill (0,0) circle (2pt);
      \draw (0,0) node[anchor=east] {\tiny$B$};
      \fill (0,1) circle (2pt);
      \draw (0,1) node[anchor=east] {\tiny$C$};
      \fill (1.3,1) circle (2pt);
      \draw (1.3,1) node[anchor=north] {\tiny$D_2$};
      \draw (1.37,-.5) node[anchor=north] {\footnotesize (5) $0<ca_1\leq a_2$};
    \end{scope}
    %(6)
    \begin{scope}[shift={(0,-5.5)}]
      \usetikzlibrary{patterns}
      \fill[black!10]  (0,3)--(1.5,2.3)--(2,0)--(0,0)--(0,3);
      \draw[thick] (0,3)--(0,0)--(2,0); 
      \draw[dashed,thick] (0,3)--(1.5,2.3)--(2,0);
      \draw[-] (-0.5,2.3) -- (3.5,2.3);
      \draw[-] (1.5,-0.25) -- (1.5,3.5);
      \fill[white] (1.5,2.3) circle (2pt);
      \draw (1.5,2.3) circle (2pt);
      \draw (1.5,2.3) node[anchor=south west] {\tiny$O$};
      \fill (2,0) circle (2pt);
      \draw (2,0) node[anchor=west] {\tiny$A$};
      \fill (0,0) circle (2pt);
      \draw (0,0) node[anchor=east] {\tiny$B$};
      \fill (0,3) circle (2pt);
      \draw (0,3) node[anchor=east] {\tiny$C$};
      \draw (1.42,-.5) node[anchor=north] {\footnotesize (6) $0<a_1<ba_2$,};
      \draw (1.46,-1) node[anchor=north] {\footnotesize \hspace{10pt} $0<a_2<ca_1$,};
      \draw (1.17,-1.5) node[anchor=north] {\footnotesize \hspace{10pt} \tiny{$(a_1,a_2):$ non-imaginary root}};
    \end{scope}
    %(6')
    \begin{scope}[shift={(5.5,-5.5)}]
      \usetikzlibrary{patterns}
      \fill[black!10]  (0,3)--(1,0.5)--(2.25,0)--(0,0)--(0,3);
      \draw[thick] (0,3)--(0,0)--(2.25,0);
      \draw[dashed,thick] (0,3)--(1,0.5)--(2.25,0);
      \draw[-] (-0.5,0.5) -- (3.5,0.5);
      \draw[-] (1,-0.25) -- (1,3.5);
      \fill[white] (1,0.5) circle (2pt);
      \draw (1,0.5) circle (2pt);
      \draw (1,0.5) node[anchor=south west] {\tiny$O$};
      \fill (2.25,0) circle (2pt);
      \draw (2.25,0) node[anchor=west] {\tiny$A$};
      \fill (0,0) circle (2pt);
      \draw (0,0) node[anchor=east] {\tiny$B$};
      \fill (0,3) circle (2pt);
      \draw (0,3) node[anchor=east] {\tiny$C$};
      \draw (1.47,-.5) node[anchor=north] {\footnotesize (6) $0<a_1<ba_2$,};
      \draw (1.51,-1) node[anchor=north] {\footnotesize \hspace{10pt} $0<a_2<ca_1$,};
      \draw (1.27,-1.5) node[anchor=north] {\footnotesize \hspace{10pt} \tiny{$(a_1,a_2):$ imaginary root}};
    \end{scope}
  \end{tikzpicture}
  \caption{Consider the points $O=(0,0)$, $A=(-a_1+ba_2,-a_2)$, $B=(-a_1,-a_2)$, $C=(-a_1,-a_2+ca_1)$, $D_1=(-a_1+ba_{2},ca_{1}-(bc+1)a_{2})$, and $D_2=(ba_{2}-(bc+1)a_{1},-a_2+ca_{1})$.  Then the support region of $x[a_1,a_2]$ can be visualized as above.} 
  \label{fig:greedy polytopes}
\end{figure}

@@

  \begin{lemma}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP(\lambda)=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    It is enough to consider $\phi_{t_{-2}}^{-1}\cC_{t_{-2}}(\phi_{t_{-2}}\lambda) \cap \cC_{t_0}(\lambda) \cap \phi_{t_2}^{-1}\cC_{t_2}(\phi_{t_2}\lambda)$, we leave the details to the reader.
  \end{proof}

  \begin{lemma}
    \label{le:one direction}
    For $\lambda\in\cI\cap\ZZ^2$, 
    \begin{enumerate}
      \item $\cP_+(\lambda):=\bigcap_{i \ge 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-b\lambda_2,\lambda_2)$.
      \item $\cP_-(\lambda):=\bigcap_{i \le 0}\phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)$ is the quadrilateral with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and $(\lambda_1,-c\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$.
    \end{enumerate}
  \end{lemma}
  \begin{proof}
    We prove (1) as (2) is obtained by interchanging $b$ with $c$ and swapping all ordered pairs.  
    We first show that $\cC_{t_0}(\lambda) \cap \phi_{t_i}^{-1}\cC_{t_i}(\phi_{t_i}\lambda)\supsetneq \cC_{t_0}(\lambda) \cap \phi_{t_j}^{-1}\cC_{t_j}(\phi_{t_j}\lambda)$ for $0\le i<j$.
  \end{proof}

  \begin{theorem}
    For $\lambda\in\cI\cap\ZZ^2$, there are five classes of dominance polytopes.
    \begin{enumerate}
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2b,-bc-\sqrt{bc(bc-4)})$ and $(2,-c)$, then $\cP(\lambda)$ is the trapezoid with corner vertices $\lambda$, $(\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$, and ???.
      \item if $\lambda$ lies on the ray spanned by $(2,-c)$, say $\lambda=(2\ell,-c\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(2\ell-\frac{bc+\sqrt{bc(bc-4)}}{2}\ell,0)$, and $(0,\frac{\sqrt{bc(bc-4)}}{b}\ell)$.
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(2,-c)$ and $(b,-2)$, then $\cP(\lambda)$ is the kite with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $\frac{bc+\sqrt{bc(bc-4)}}{2\sqrt{bc(bc-4)}}(2\lambda_1+b\lambda_2,c\lambda_1+2\lambda_2)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2)$.
      \item if $\lambda$ lies on the ray spanned by $(b,-2)$, say $\lambda=(b\ell,-2\ell)$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(-\frac{\sqrt{bc(bc-4)}}{c}\ell,0)$, and $(0,\frac{bc+\sqrt{bc(bc-4)}}{2}\ell-2\ell)$.
      \item if $\lambda$ lies in the interior of the cone spanned by the vectors $(b,-2)$ and $(2b,-bc+\sqrt{bc(bc-4)})$, then $\cP(\lambda)$ is the triangle with corner vertices $\lambda$, $(\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2,0)$, $(0,-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2)$, and ???.
    \end{enumerate}
  \end{theorem}
  \begin{proof}
    Following Lemma~\ref{le:one direction}, we see that the intersection $\cP_+(\lambda)\cap\cP_-(\lambda)$ degenerates to a triangle precisely when
    \[\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_1-\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2=\lambda_1+\frac{bc+\sqrt{bc(bc-4)}}{2c}\lambda_2\]
    or 
    \[\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\lambda_2=-\frac{bc+\sqrt{bc(bc-4)}}{2b}\lambda_1+\frac{2-bc-\sqrt{bc(bc-4)}}{2}\lambda_2.\]
    The first equations reduces to $c\lambda_1+2\lambda_2=0$, while the second reduces to $2\lambda_1+b\lambda_2=0$.
    In particular, the rays spanned by $(2,-c)$ and $(b,-2)$ determine this change of state in the dominance regions $\cP(\lambda)$.
  \end{proof}
